Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-18 paper/main.tex
Cut on Sengupta details

% AD intro
Second, we analyzed data from the audio-description offering exclusively
auditory stimulation.
% AD primary contrast
The primary $t$-contrast for the audio-description (\texttt{geo, groom} >
non-spatial noun categories) yielded six significant clusters
(Tab.~\ref{tab:res-ao-group1}, Fig.~\ref{fig:group-slices}).
% overlap with ROI
Two homologous clusters are located in the anterior part of the PPA group
overlap.
% in detail
Specifically, these clusters are located at the borders of the posterior
parahippocampal cortex, the occipital and temporal fusiform gyrus and lingual
gyrus.\todo{Havard-Oxford atlas: 3 different most prob. locations depen. on
voxel}
% precuneus
Two additional homologous clusters are apparent in the ventral precuneus
extending into the retrosplenial cortex.
% LOC
Finally, two homologous clusters are located in the superior lateral occipital
cortex.

@@

% intro
Third, we investigated result from both naturalistic paradigms on the level of
individual participants to ensure that the group results are not just a by-product
of the averaging process.
% AD is the real shit
Further, we hypothesized that an exclusively auditory stimulus could localize
the PPA in individual participants and thus possibly substitute a classic visual
localizer experiment.
% Sengupta et al., 2016; unilateral in sub-04 and sub-20
The visual localizer yielded bilateral parahippocampal clusters in 12 of 14
participants and an unilateral right clusters in two participants (Tab.~3 in
\citep{sengupta2016extension}).
% Sengupta: 1 of 3
Individual PPAs were assessed by visually inspecting thresholded $t$-maps
($Z$>1.64, $p$<.05 cluster corrected) of three different $t$-contrasts, and
titrating\todo{??} the $t$-threshold in the range of [2, 3] in until we found an
isolated cluster (Tab.~3 in that matched the expected anatomical location
based on literature \citep{epstein1998ppa}.

% one contrast to localize them all; "...and $Z$>3.4 for all"
Contrary to \citep{sengupta2016extension}, we here used the same contrast of
each naturalistic stimulus and the same threshold for all participants.
% subject space -> NeuroVault
Results of the analyses that were performed in participant-space can be found in the
accompanying dataset ($Z$>2.3, $p$<.05 cluster-corrected).
% here report in group space
For better comparisons of participants, we here report results from the analyses
performed in group space ($Z$>3.4, $p$<.05 cluster-corrected).
% ref to figure
Figure~\ref{fig:subs-thresh-ppa} depicts thresholded $Z$-maps of the primary movie
and audio-description $t$-contrast, and the outline of overlapped, individual PPAs
co-registered to the MNI152 template.
% one slice to show them all
Transversal slice of $Z$=-11 was chosen as it depicts voxels of
significant clusters in almost all participants.

>>>>

% AD intro
Second, we analyzed data from the audio-description offering exclusively
auditory stimulation.
% AD primary contrast
The primary $t$-contrast for the audio-description (\texttt{geo, groom} >
non-spatial noun categories) yielded six significant clusters
(Tab.~\ref{tab:res-ao-group1}, Fig.~\ref{fig:group-slices}).
% overlap with ROI
Two homologous clusters are located in the anterior part of the PPA group
overlap reported by \cite{sengupta2016extension}.
% in detail
Specifically, these clusters are located at the borders of the posterior
parahippocampal cortex, the occipital and temporal fusiform gyrus and lingual
gyrus.
% precuneus
Two additional homologous clusters are apparent in the ventral precuneus
extending into the retrosplenial cortex.
% LOC
Finally, two homologous clusters are located in the superior lateral occipital
cortex.

@@

% intro
Third, we inspected results from both naturalistic paradigms on the level of
individual participants, and compared them to the individual PPA localizations
provided by \cite{sengupta2016extension}, who reported
% Sengupta et al., 2016; unilateral in sub-04 and sub-20
bilateral parahippocampal clusters in 12 of 14
participants and a unilateral right clusters in two participants
\citep[Tab.~3 in][]{sengupta2016extension}.
% one contrast to localize them all; "...and $Z$>3.4 for all"
Unlike \cite{sengupta2016extension}, who determined PPA clusters using three
candidate contrasts and a variable threshold, we used a single contrast for
each naturalistic stimulus and a uniform threshold for all participants.
% subject space -> NeuroVault
Results of the analyses that were performed in participant-space can be found in the
accompanying dataset ($Z$>2.3, $p$<.05 cluster-corrected).
% here report in group space
For better comparisons of participants, we here report results from the analyses
performed in group space ($Z$>3.4, $p$<.05 cluster-corrected).
% ref to figure
Figure~\ref{fig:subs-thresh-ppa} depicts thresholded $Z$-maps of the primary movie
and audio-description $t$-contrast, and the outline of overlapped, individual PPAs
co-registered to the MNI152 template.
% one slice to show them all
Transversal slice of $Z$=-11 was chosen as it depicts voxels of
significant clusters in almost all participants.
